Exploring Homicide Trends in Toronto: A Seventeen-Year Statistical Overview (2004-2020)

### 2024-01-19 outputs/paper/paper.qmd
code fix

---
```{r}
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
```

```{r}
library("janitor")
library("tidyverse")
library("knitr")
```

>>>>

---
```{r}
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
library("janitor")
library("tidyverse")
library("knitr")
```
